Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
Work on the ba.

\documentclass[11]{article}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{comment}
\hypersetup{pdftex,colorlinks=true,allcolors=blue}
%\usepackage{hypcap}
\usepackage[url=true,doi=false,isbn=false,backend=biber]{biblatex}
\addbibresource{managed.bib}
%\setcounter{tocdepth}{2}
%\usepackage{pdfpages}
%\usepackage{wrapfig}
%\makeatletter
%\newcommand{\setword}[2]{%
%    \phantomsection%
%    #1\def\@currentlabel{\unexpanded{#1}}\label{#2}%
%}
%\makeatother

@@

>>>>

\input{header}

@@

\section{Leaderless Algorithms}

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$ and equipped with a dependency relation $R \subseteq C\times C$ such that for any command $c$, $\left( c,c \right)\notin R$; for any commands $c_1$ and $c_2$, if $\left( c_1,c_2 \right)\in R$ then $\left( c_2,c_1 \right)\in R$; if $\left( c_1,c_2 \right)\in R$ and $\aseq{s_1,c_1,s_2,c_2,\cdots,s_n}$

\subsection{Computing Dependency-Sets}

A dependency-set computation algorithm allows processes to announce a command $c$ and to learn about a suggested dependency set for a previously announced command.

A dependency-set computation algorithm exposes the input actions ${announce\left( c \right)}^p$, where $c$ is a command, and the output actions ${suggest\left( c, deps \right)}^p$, where $c$ is a command and $deps$ is a set of commands.
Moreover, a dependency-set computation algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, deps \right)}$, the command $c$ must have been announced before.
    \item for any two suggestions $suggest\left( c_1, deps_1 \right)$ and $suggest\left( c_2, deps_2 \right)$,  if $c_1$ and $c_2$ do not commute then either $c_1\in deps_2$ or $c_2 \in deps_1$.
\end{itemize}

\subsection{Agreeing on Dependency Sets}

A map-agreement algorithm exposes
